Project Review

### 2024-04-26 Review_by_Kelly_Cao/Project_Review.qmd
Project Review-KellyCao

---
title: Project Review Template 
author: MALIKA DHAKHWA
date: 4/25/2024
format: 
  html:
    toc: true
    toc-depth: 3
    number-sections: true
---

@@

Name of project reviewer: Malika Dhakhwa

# Specific project content evaluation
Evaluate the different parts of the project by filling in the sections below.

@@

### Feedback and Comments
You have effectively set the objective and contextualized the project within existing literature, showing how your work aligns with prior studies. I recommend adding a brief overview on the broader importance of sleep quality, such as its impact on health and daily performance, to explain the relevance of your study.

The end of section 2.1 (Background Information) mentions that your study expect to see trends where increased stress levels negatively impact sleep quality and sleep duration. It creates some confusion whether sleep duration is also an outcome variable of the study. I would recommend making necessary adjustments for the clarity of your research focus.

@@

### Feedback and Comments
Your hypothesis that stress, sleep duration, and occupation would have the largest impact on sleep quality is clearly stated. It is well formulated using the preliminary data analysis.

@@

### Feedback and Comments
You have outlined the data and its variables in the Abstract and Data Processing sections. The data and units of measurement of the variables are clearly explained in the exploratory data analysis (EDA) file. For greater clarity, it would be beneficial to mention the units of measurement in the manuscript as well.

I was unable to find a codebook. The provided data link leads to the general Kaggle datasets page rather than directly linking to your specific dataset.

@@

### Feedback and Comments
You have done a great job in performing and explaining the data cleaning, processing and exploring.

While you have described the methods used for feature engineering, detailing the levels of the new factor variables 'cat_bp', 'StepsGroup', and 'PhysicalActivityGroup' would further clarify your methods.

@@

### Feedback and Comments
The use of Random Forest (RF) analysis appears well-suited to the dataset. You have also employed the appropriate performance measures, variable selection techniques, data pre-processing steps, and model evaluation strategies.

However, there is limited explanation regarding the decision to apply GLM to each predictor separately and not to use it in a model including all predictors. Additionally, I would recommend detailing the rationale for comparing only the null model with the RF model.

@@

### Feedback and Comments
You have made a good use of the figures and tables in the manuscript to help visualize the data and understand the results. Overall, the presentation of results is commendable, with clear and accessible tables and figures.

The readability of tables could be further improved by limiting the number of decimal places displayed. This would make the tables less cluttered.

For categorical variables, I would recommend to include the reference categories in parentheses (e.g., BMI.CategoryObese(Ref.: Normal)) directly in the results tables. This addition would clarify the comparisons being made, creating an ease in interpreting the results.

I noticed a discrepancy in the explanation of Figure 3, where the RMSE is described as increasing and the R-squared as decreasing with the addition of more predictors.

@@

### Feedback and Comments
You have thoroughly explained the findings of your study in the discussion section, clearly acknowledging both its strengths and limitations. To enhance the robustness of your discussion, I would recommend addressing the fact that the data was not split into training and testing subsets, which is a common practice for assessing model generalizability.

@@

## Further comments
In your statistical-analysis.R file, at line 199, I believe there is a misunderstanding in the interpretation of the results. It is mentioned that the intercept indicates that being unemployed results in a sleep quality score of about 7. However, it seems that this interpretation actually pertains to the reference category of Business/Finance instead of the unemployed category.

# Overall project content evaluation
Evaluate overall features of the project  by filling in the sections below.

@@

### Feedback and Comments
You have done a great job in organizing your project, with files generally placed in well-labeled folders with the exception for figures. They are located in the images folder within the product folder, which differs from what is described in the main ReadMe file.

@@

### Feedback and Comments
You have done a great job with documentation of the project. Especially in the eda and analysis code files, each phase and the decisions behind each step are well commented. Anyone reviewing your project can easily follow and comprehend the entire analysis process.

@@

### Feedback and Comments
Your project stands out in reproducibility. The documentation clearly explains how to replicate the analysis without the need of any manual intervention. I was able to re-run the entire analysis without any issues.

@@

### Feedback and Comments
Your study addresses its hypotheses using the Random Forest model. However, incorporating comparisons with other advanced machine learning tools, such as LASSO, could provide a more comprehensive analysis. Additionally, enhancing the validation process by splitting the data into training and testing subsets would strengthen the robustness and generalizability of your findings.

@@

## Further comments
- Consider organizing all library import statements at the top of your statistical-analysis.R script. 
- Refine your references and in-text citation of the link 10,000 steps.org

>>>>

---
title: Project Review 
author: Kelly Cao
date: 04/26/2024
format: 
  html:
    toc: true
    toc-depth: 3
    number-sections: true
---

@@

Name of project reviewer: Kelly Cao

@@

### Feedback and Comments

The background was well described with plenty of notable references. It's comprehensive and pairs well with the study you guys implemented. Your background clearly note the important predictors for sleep quality, while also pairing it with many references to different studies.

Although, I did have some confusion with how you mentioned conflicting references at the end. Perhaps, you can bring some more clarity for the direction you wish to support or if that's another question you wish to answer.

@@

### Feedback and Comments

While reading you background, I understand you guys were hoping to study the relationship between the many predictors listed and quality of sleep. This was easily determined.

@@

### Feedback and Comments

Although it is unfortunate you guys were unable to determine the source of the data set, you guys clearly noted where in Kaggle you discovered it and why you still proceeded to use this set. I note that you guys mentioned a codebook in your manuscript, but I was unable to find it in your repository or in the Kaggle link provided.

@@

### Feedback and Comments

It appears that the raw data set was fairly clean from the get-go. You guys clearly documented any changes you made to it and the new variables added. I would suggest cleaning up some of the formatting issue in your data section, as it made it somewhat difficult to read.

@@

### Feedback and Comments

You guys used the appropriate models for the study. The dataset is well-suited for Random Forest (RF) analysis, especially considering its classification nature, which aligns perfectly with the strengths of RF in handling such problems. Additionally, the use of the simple linear regression model was a great step in determining major predictors to focus on.

@@

### Feedback and Comments

The figures and tables are super clear and easy to read. I felt that you chose the best images to represent the data and the analysis you provided.

I particularly enjoyed the colinearity plot and the observed vs prediction plots, as I felt they provided the most information.

@@

### Feedback and Comments

The strengths and limitations were clearly mentioned. The limitation being the dataset, and the strength being the easy and clear interpretation of the data set.

@@

## Further comments
It appears that the project is practically finished. You guys just need to clean up your manuscript and include the references.

@@

### Feedback and Comments

The repository was clean and neat. The README files were clear in the description. The files were reasonably named. It seems all of the junk files were properly removed.

@@

### Feedback and Comments

It appears everything is properly documented. Your code was easy to follow. As a personal preference, I would enjoy having the statistical analysis be performed in a quarto document, as it would allow me to render and view it in a more digestable format.

@@

### Feedback and Comments

All of the major components of your project was easily reproducible. I started off the review by quickly running through each of your codes and major documents to see if it would run and render. However, since you mentioned your Supplementary-Material.qmd in a README.qmd, I went to see it and ran into a problem of rendering it and got this error:

```
processing file: Supplementary-Material.qmd
  |....                                               |   8% [unnamed-chunk-2] 
Quitting from lines 73-74 [unnamed-chunk-2] (Supplementary-Material.qmd)
Error:
! object 'sleepdata' not found
Backtrace:
 1. base::print(sum(is.na(sleepdata)))

Execution halted
```

If you are showing supplementary exploratory analysis, I would recommend using the `read_chunk()` function, as it will allow you to pull specific lines from a .R script with some specific formatting. If that wasn't the intended goal, I would also suggest you saving the data-frame/data-set you intend to work across different files, as it would make things easier for other people to access. The error seems to indicate that the object you are referencing is not found in the environment we are working with.

I'm not sure if this was an issue on my end, but when attempting to source your analysis .R script, this error would pop up:

```
+ library(broo .... [TRUNCATED] 
Error in -library(broom) : invalid argument to unary operator
```
The other lines after that ran perfectly fine.

Other than that, all of the remaining codes and documents ran easily and matched the .html output file.

@@

### Feedback and Comments

The study was performed very well, but I imagine it can be strengthened further with additional analysis, using different models for comparison. I would also like to see further assessment on your model with cross validation studies to further prove the robustness of your model.

Despite that, I felt the hypotheses were addressed properly.

@@

## Further comments
Minor issues noted above:

 - Formatting issue in data section of manuscript
 - References in manuscript
 - Supplementary markdown file 
 - Missing codebook

Overall, I felt the study was thorough and nicely documented. Everything was easy to follow, and there were little to no issue with going through your repository.
